Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-09 edubots_surveys.Rnw
Rephrasing sentence about clarification of RQ1
Addresing another reviewer's comment
Rephrasing about teachers in Humanities
Addresing another comment

This is why for answering RQ1, teachers were queried about whether they use
messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an
application used mainly in IT departments and software development), or any
other messaging app, and whether they use messaging apps provided by their
academic institution (see Table \ref{tab:use_messapps}). In this case, it is
maybe in order a certain clarification. While we had in mind, as indicated by
the possible answers, instant messaging applications when making this question,
we included these institution-provided applications mainly for completion. But
it should be noted that, in most cases, they are not {\em instant} messaging
apps in the way Telegram or Facebook Messenger are; in most cases they are
messaging facilities provided by learning management systems such as (usually)
Moodle. So the answer to this question must be understood in two different ways:
their preference for the {\em source} of the technology (university, any
company) as well as the {\em type} of technology (instant, app based messaging
systems vs. web-based systems integrated in another learning management system).

@@

% Fran: I think figures with data about the use of messaging apps should come here. Then, we say we also asked about changes after covid and include data about that
Results in Figs. \ref{figure:provided*chatbots_use},
\ref{figure:whatsapp*chatbots_use}, \ref{figure:telegram*chatbots_use} do not
show significant differences in the use of instant messaging apps between
teachers from University and vocational education. In general, most teachers
prefer messaging apps provided by their own institutions (we also show the
results for the two most popular messaging app platforms: WhatsApp and
Telegram). With respect to specific disciplines, Engineering and Technology
teachers are more active in their use, although it is also relevant the amount
of teachers from Humanities that answered they used these apps in their classes
(around 60\% use the apps provided by their institutions).

>>>>

This is why for answering RQ1, teachers were queried about whether they use
messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an
application used mainly in IT departments and software development), or any
other messaging app, and whether they use messaging apps provided by their
academic institution (see Table \ref{tab:use_messapps}). In this case, we would like 
to add a clarification. While we had in mind, as indicated by the possible answers, 
instant messaging applications when making this question,
we included these institution-provided applications mainly for completion. But
it should be noted that, in most cases, they are not {\em instant} messaging
apps in the way Telegram or Facebook Messenger are; in most cases they are
messaging facilities provided by learning management systems such as (usually)
Moodle. So the answer to this question must be understood in two different ways:
their preference for the {\em source} of the technology (university, any
company) as well as the {\em type} of technology (instant, app based messaging
systems vs. web-based systems integrated in another learning management system).

@@

% Fran: I think figures with data about the use of messaging apps should come here. Then, we say we also asked about changes after covid and include data about that
Results in Figs. \ref{figure:provided*chatbots_use},
\ref{figure:whatsapp*chatbots_use}, \ref{figure:telegram*chatbots_use} do not
show significant differences in the use of instant messaging apps between
teachers from University and vocational education. In general, most teachers
prefer messaging apps provided by their own institutions (we also show the
results for the two most popular messaging app platforms: WhatsApp and
Telegram). With respect to specific disciplines, Engineering and Technology
teachers are more active in their use, but the amount of teachers from Humanities 
who answered they used these apps in their classes is also remarkable
(around 60\% use the apps provided by their institutions).
